\vspace{-0.2cm}
\cvsection{Experience}

\begin{cventries}
  \cventry
    {\textbf{Software Engineer (Quant Systems SRE)}} % Job title
    {DE Shaw and Co.} % Organization
    {Hyderabad, India} % Location
    {July 2019 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{\textit{Kafka adoption for incident-response systems:}} As a monitoring SME, redesigned event processing engine to facilitate event-sourcing with Kafka; bumped up the maximum event coverage capacity (SLO) upto  \underline{\texttt{\char`\~}2 million events/day}.
        }
        \vspace{0.1cm}
        \item {\textbf{\textit{Web-service deployment framework:}} Implemented a service deployment framework in Puppet and Kubernetes-Helm to deploy highly-available web-services with \textit{Service Registration mechanism}, NGINX setup for TLS \& HTTP proxying (Ambassador pattern) as well as a log-shipping ElasticSearch-Filebeat component for analytics.
        }
        \vspace{0.1cm}
        \item {\textbf{\textit{Release Engineering:}} Conducted enterprise and DMZ Linux server patching and releases -- servers that run ElasticSearch cluster,  Vault secret store, and core infra services such as DNS, Puppet and Kerberos.
        }
        \vspace{0.1cm}
        \item {\textbf{\textit{Container registry and universal artifact repository deployment:}} Deployed and maintained a multi-site, multi-clustered, highly-available on-prem Universal Artifact Repository with Anycast routing for low-latency package uploads and downloads. Directly Responsible Individual for this system serving \underline{more than 600K} artifacts with \textit{three 9s level of availability SLO.}
        }
      \end{cvitems}
    }
  \cventry
    {\textbf{Systems \& Operations Engineering intern}} % Job title
    {DE Shaw and Co.} % Organization
    {Hyderabad, India} % Location
    {May 2018 - June 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{\textit{Linux grid job submission infra:}} Improved fault-tolerance of 6 different \textit{Apache Mesos} masters by \underline{50\%} with \textit{streaming replicas} using \textbf{\emph{Postgres Patroni}} framework in a newly created hypercluster; saved \textit{19\%} monthly error-budget of the in-house Mesos PaaS.
        }
        \vspace{0.1cm}
        \item {\textbf{\textit{Systems Opsconsole:}} Analyzed tickets and system-wide issues reported for better operational efficiency. Built visualizations to provide insights. 
        }
        \item {Designed and developed a Web-app with React front-end, Python backend and DE Shaw proprietary JavaScript libraries.
        }        
        \item {On top of reducing \textit{MTTD (Mean Time To Detect)}, the project also reduced \textit{MTTR (Mean Time To Repair)} taken by SREs to fix users' NFS home directories, grid job submissions, active sessions and group memberships by \underline{19\%}.
        }
        \vspace{-0.3cm}
      \end{cvitems}
    }
%   \cventry
%     {\textbf{Lead Backend Engineer}} % Job title
%     {\newline Skyline Labs} % Organization
%     {\newline Pune, India} % Location
%     {2015 - 2018} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Had a major role to play in conceptualizing the \textbf{\textit{design process and technology stack}} of multiple web-based projects}
%         \item {Part of the multiple awards winning \textit{project Find-X} and \textit{project Orola}: aimed to increase efficiency of urban public transportation and digital healthcare solution in remote Indian villages.}
%       \end{cvitems}
%     }
\end{cventries}
